The Aquarius Stream Progenitor Was Not a Globular Cluster

### 2012-11-21 2012-aqs/draft-aqs.tex
Inserted figure

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. In order to exclude saturated lines we only used lines with a reduced equivalent widths $\log_{10}{(\mbox{EW}/\lambda)} < -4.5$ in our chemical abundance analysis. A minimum detectable equivalent width was measured as a function of wavelength, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD122563 and comparing our measurements with the study of \citet{Norris;et-al_2000}. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $X.X \pm X.X$\,m\AA{}, and no systematic trend is present.

% equivalent widths plot with Norris for HD 122563

>>>>

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. In order to exclude saturated lines we only used lines with a reduced equivalent widths $\log_{10}{(\mbox{EW}/\lambda)} < -4.5$ in our chemical abundance analysis. A minimum detectable equivalent width was measured as a function of wavelength, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD140283 and comparing our measurements with the study of \citet{Norris;et-al_2000}. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{The gold standard comparison.}
	\label{fig:ew-compare}
\end{figure}
